Supplementary Information for Diverse lithic production strategies in southwest China during Late Middle Pleistocene

### 2021-06-25 analysis/paper/paper.Rmd
working through the SI
updates and checking of manuscript and SI

file_name <- here::here("analysis/data/raw_data/artefacts-after Sam_Dec2018_quina_modified.xls")

@@

Results of descriptive statistics for Levallois and non-Levallois flakes. ‘PLF’ stands for preferential Levallois flake; ‘CF’ stands for complete flake.

@@

Are CV values lower for Levallois flakes than for non-Levallois flakes?

@@

## calculate GIUR

# get tn
df_giur_tn <- retouch[, c(1,8,10,12,14,16,18,20,22)]

# divide tn by Tn
df_giur <- df_giur_tn[, -1] / retouch[, c(9,11,13,15,17,19,21,23)]

# compute GIUR as average of all zones
df_giur_values <- 
df_giur %>% 
  as_tibble %>% 
  rowwise %>% 
  mutate(GIUR = mean(c_across(section_1_t:section_8_t), 
                     na.rm = TRUE)) %>% 
  select(GIUR)

df_giur_values$number <- df_giur_tn$number

df_giur_clustered <- 
  left_join(df_giur_values, 
            flakes_clustered[, c("number", "cluster")]) %>% 
  drop_na() %>% 
  filter(GIUR <= 1)

df_giur_clustered$quina <- ifelse(df_giur_clustered$number %in% quina_id, "Quina", "Non-Quina")

df_giur_clustered_tt_test <- 
df_giur_clustered %>% 
    t.test(data = ., 
           GIUR ~ quina) %>% 
      apa_print %>% 
      .$statistic %>% 
  str_remove_all("\\$|\\{|\\}|\\\\|mathit")

@@

compare_qui_non_qui_giur_plot <-
  ggplot(df_giur_clustered) +
  aes(y = GIUR,
      x = quina) +
  geom_flat_violin(position = position_nudge(x = .25, 
                                             y = 0), 
                   alpha = .8,
                   adjust = 0.35)  +
  geom_quasirandom( 
             size = .75, 
             width = 0.25,
             alpha = point_alpha) +
  geom_boxplot(
        width = .25, 
               outlier.shape = NA, 
               alpha = 0.25
               ) +
  ggtitle(paste0("Flake GIUR: ", df_giur_clustered_tt_test)) +
  coord_flip() +
  theme_bw() +
  ylab("GIUR") +
  xlab("")

@@

Plot combining multiple panels

>>>>

file_name <-
  here::here("analysis/data/raw_data/artefacts-after Sam_Dec2018_quina_modified-2019.xls")

@@

Results of descriptive statistics for Levallois and non-Levallois flakes. ‘PLF’ stands for preferential Levallois flake; ‘CF’ stands for complete flake. This is table 1 in the main text

@@

Are CV values lower for Levallois flakes than for non-Levallois flakes? This result is presented in line in the text in the main text.

@@

## calculate GIUR
# looking at the GIUR data... there are some duplicate artefact numbers, which is a nuisance

# make the number ID unique
retouch$number <- make.unique(as.character(retouch$number), sep = "_")

retouch_giur_per_section <-
  retouch %>%
  dplyr::select(grep("^number$|_t|_T", names(retouch))) %>%
  gather(variable, value, -number) %>%
  separate(variable, c("section", "tee"), sep = 10) %>%
  pivot_wider(names_from =  tee, values_from = value) %>%
  mutate(t_T = t / T)  %>%
  filter(t_T <= 1)

retouch_giur_per_artefact <-
  retouch_giur_per_section %>%
  group_by(number) %>%
  summarise(mean_giur = mean(t_T, na.rm = TRUE)) %>% 
  mutate(quina = ifelse(number %in% quina_id, "Quina", "Non-Quina"))

df_giur_clustered_tt_test <- 
retouch_giur_per_artefact %>% 
    t.test(data = ., 
           mean_giur ~ quina) %>% 
      apa_print %>% 
      .$statistic %>% 
  str_remove_all("\\$|\\{|\\}|\\\\|mathit")

@@

compare_qui_non_qui_giur_plot <-
  ggplot(retouch_giur_per_artefact) +
  aes(y = mean_giur,
      x = quina) +
  geom_flat_violin(position = position_nudge(x = .25, 
                                             y = 0), 
                   alpha = .8,
                   adjust = 0.35)  +
  geom_quasirandom( 
             size = 1.5, 
             width = 0.25,
             alpha = point_alpha) +
  geom_boxplot(
        width = .25, 
               outlier.shape = NA, 
               alpha = 0.25
               ) +
  ggtitle(paste0("Flake GIUR: ", df_giur_clustered_tt_test)) +
  coord_flip() +
  theme_bw() +
  ylab("GIUR") +
  xlab("")

@@

Plot combining multiple panels, this is Figure 1 is the main text
